\documentclass[conference]{IEEEtran}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% ===============================================================
\usepackage{subfigure, graphicx, booktabs}
%\usepackage{algpseudocode, algorithmicx, algorithm}
\usepackage{multirow, amsmath, amsthm, listings, booktabs}

% ===============================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
%\newdef{definition}[theorem]{Definition}
%\newdef{remark}[theorem]{Remark}


\begin{document}
\title{An Efficient Collaborative Filtering Approach Using Smoothing and Fusing}


% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Xin Liu, Daqiang Zhang, Jingyu Zhou, Minyi Guo, Yao Shen}
\IEEEauthorblockA{Department of Computer Science\\
Shanghai Jiao Tong University\\
No. 800, Dongchuan Road, Shanghai, P.R.China\\
\{navyliu, zhangdq\}@sjtu.edu.cn, \{guo-my, zhou-jy, shen\_yao\}@cs.sjtu.edu.cn}
}

% make the title area
\maketitle


\begin{abstract}
In advent of multicore era, plain C/C++ programming language can not
fully reflect computer architectures. Source-to-source
transformation helps tailor programs close to contemporary
hardwares. In this paper, we propose a template-based approach to perform 
transformation for programs with rich static information.
The template metaprogramming techniques we present can conduct
parallelization and memory hierarchical optimization for specific multicores. They enable
programmers to utilize new architectural
features and parallel patterns by extending template library. 
We implement a prototype template library -- libvina
to demonstrate the idea. Finally, We evaluate our template library on
commodity x86 and GPU platforms by a variety of typical applications
in multimedia and scientific fields. In experiments, we show that our
approach is flexible to support multiple parallel models and capable
of transforming sequential code to parallel equivalence  according to
specific multicore architectures. Moreover, the cost of programmability using our
approach to adapt more than one multicore platform is manageable.
\end{abstract}

% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle


\input{intro.tex}
%\input{related.tex}
%\input{background.tex}
\input{method.tex}
%\input{evaluation.tex}
%\input{conclusion.tex}
%\input{acknowledge.tex}

\bibliographystyle{ieeetran}
\bibliography{instructions}



% that's all folks
\end{document}
